Long-term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-08-27 article/article.Rmd
Commit 2024-08-27 11:10

The duration of the CE events is variable and can last for several minutes or even
more than an hour. In order to study the characteristics of these consecutive events,
we grouped them into bins of increasing duration in steps of one minute.  We have
identified `r ST_G0[, .N]` groups of CE in the whole period of study, where the group
of the longest duration of
`r ST_G0[, max(GLB_diff.N)]` minutes occurred on
`r strftime(ST_G0[which.max(GLB_diff.N), Date], "%d\\ %B %Y")`.
Figure\nobreakspace{}\ref{fig:ceg-duration-distribution} shows the frequency
distribution of the CE events according to their duration.  We conclude that although
some groups of events last for more than an hour, about $80\,\%$ have duration of
less than 5 minutes.

@@

An aspect of the CE events that is commonly reported and has some significance on the
solar energy production infrastructure are the extreme CE events (ECE), where solar
irradiance exceeds the expected irradiance on top of the atmosphere at the same SZA
(Equation\nobreakspace{}\ref{eq:ECE}).  Analogous to
Figure\nobreakspace{}\ref{fig:relative-month-occurrences} we have computed the
distribution of the number of occurrences of ECE events by month in
Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE}. The most active period
for ECE events is in spring and early summer (March -- June), followed by a
period in late autumn (September and October).  This is probably related to the
weather characteristics in these periods, with frequent alternations between clear
sky periods and clouds.

>>>>

The duration of the CE events is variable and can last for several minutes or even
more than an hour. In order to study the characteristics of these consecutive events,
we grouped them into bins of increasing duration in steps of one minute.  We have
identified `r ST_G0[, .N]` groups of CE in the whole period of study, where the group
of the longest duration of
`r ST_G0[, max(GLB_diff.N)]` minutes occurred on
`r strftime(ST_G0[which.max(GLB_diff.N), Date], "%d\\ %B %Y")` in a SZA range of 
$`r round(ST_G0[which.max(GLB_diff.N), SZA.min],1)`^\circ$ -- 
$`r round(ST_G0[which.max(GLB_diff.N), SZA.max],1)`^\circ$.
Figure\nobreakspace{}\ref{fig:ceg-duration-distribution} shows the frequency
distribution of the CE events according to their duration.  We conclude that although
some groups of events last for more than an hour, about $80\,\%$ have duration of
less than 5 minutes.

@@

An aspect of the CE events that is commonly reported and has some significance on the
solar energy production infrastructure are the extreme CE events (ECE), where solar
irradiance exceeds the expected irradiance on top of the atmosphere at the same SZA
(Equation\nobreakspace{}\ref{eq:ECE}).  Analogous to
Figure\nobreakspace{}\ref{fig:relative-month-occurrences} we have computed the
distribution of the number of occurrences of ECE events by month in
Figure\nobreakspace{}\ref{fig:relative-month-occurancies-ECE}. The most active period
for ECE events is in spring and early summer (March -- June), followed by a
period in early autumn (September and October).  This is probably related to the
weather characteristics in these periods, with frequent alternations between clear
sky periods and clouds.
